---
title: "Assignment 05"
author: "Neil Noyes"
date: "9/19/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1

Load libraries
```{r}
library(tidyverse)
library(here)
```

Store path to dataset
```{r}
store_data_path <- here("Datasets", "msft.csv")
```

Read in data
```{r}
store_data <- read_csv(store_data_path)
```

Configure col_types (Price changed to col_number from col_character)
```{r}
store_data <- read_csv(store_data_path,
                        col_types = cols(
                                          Name = col_character(),
                                          Rating = col_double(),
                                          `No of people Rated` = col_double(),
                                          Category = col_character(),
                                          Date = col_character(),
                                          Price = col_number()
                                        )
                       )
```

And take a look
```{r}
str(store_data)
```

We see that the string "Free" is used for price for free applications, which then leads to the column being read as NA as a parse error, so we will replace these with 0.0's
```{r}
store_data <- store_data %>%
  mutate(
    Price = ifelse(is.na(Price),
                    0.0,           
                    Price        
    )
  )
```

<span style="color: green; font-size: 14pt">Did you double check that *all* the NAs are as a result of the "Free" string, or are there any other causes?</span> 

Now we see the change
```{r}
str(store_data)
```

## Problem 2

If we look at one variable...

We can take a look at the distribution of ratings for apps on the Windows store:
```{r}
store_data %>%
  ggplot() +
  geom_bar(aes(x = Rating), width = 0.5, fill = "#FF6666") +
  ggtitle("Distribution of Application Ratings") +
  xlab("Rating (1-5)") +
  ylab("# Ratings")
```

We see here that most ratings in the Windows store are fairly positive. 

<span style="color: green; font-size: 14pt">I'm not so sure about setting the width here. This lead to think this was a histogram, and that the ratings were more continuous.</span> 

## Problem 3

Now with two variables... 

Lets look at the average rating per category!
```{r}
store_data %>%
  ggplot() +
  geom_boxplot(aes(x = Category, y = Rating)) +
  theme(axis.text.x = element_text(angle = 90)) +
  ggtitle("Distribution of Ratings by Category")
```

Here we see a solid average of 4 stars for every category except multimedia design.. I guess those people have bad apps. 

<span style="color: green; font-size: 14pt">Interesting.  Although there's some differences in variability for some catgories.</span> 

